Manuscript_Github_Pchabaudi_boilerplate

### 2022-07-30 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_TPMheatmaps.Rmd
Alter dimensions of saved heatmap

if(global_save_var){
  pdf(file = 'plots/subfam_TPMheatmap.pdf',
      height = 5,
      width = 8)
  draw(ht.list, 
       row_title_side = 'left',
       column_title_side = 'bottom',
       heatmap_legend_side = 'right',
       merge_legend = TRUE)
  dev.off()
}
```

>>>>

if(global_save_var){
  pdf(file = 'plots/subfam_TPMheatmap.pdf',
      height = 8,
      width = 6)
  draw(ht.list, 
       row_title_side = 'left',
       column_title_side = 'bottom',
       heatmap_legend_side = 'right',
       merge_legend = TRUE)
  dev.off()
}
```
